% Jason Stelzer's Resume
% Created: 5 May 2010
% Last Modified: 20 May 2010

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Jason Stelzer}
\newcommand{\addr}{532 Arbor Rd, Cheltenham, PA 19012}
\newcommand{\phone}{(484) 431-5866}
\newcommand{\email}{jason.stelzer@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{objsection}[1]{
  \vspace{4pt}
  {\fontfamily{phv}\selectfont\Large#1}
  
  \vspace{3pt}
}
  

\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

\vspace{8 pt}




%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}
	\begin{ressubsec}{Health Market Science}{King of Prussia, PA}{Software Developer/Technical Lead: July 2003--present}

	  \ressubitem{Developed algorithms to automate the
            standardization, matching, and integration of 5,000
            incoming data sources representing 20 MM unique entities
            across 4 TB of data.  Software used a custom distributed
            processing engine to implement fuzzy matching algorithms
            that ranged from simplistic fuzzy matching
            (e.g. Levenshtein edit distance) to complex multi-step
            criteria. }

	  \ressubitem{Created clustered application to create an
            address standardization/geocoding service as a centralized
            service for core HMS applications.}

	  \ressubitem{Created and designed software to facilitate
            moving from a large, legacy code base to a more granular
            SOA architecture composed of loosely coupled applications
            such that components could be reused and shared across
            applications.}

	  \ressubitem{Created documentation and tutorials to assist in
            training new employees and share expertise with existing
            staff.}

	  \ressubitem{Designed and developed J2EE applications to
            augment our core Reference Data projects and custom
            solutions for clients needing assistance assimilating our
            data.}

	  \ressubitem{Designed and developed the infrastructure for
            integrating our legacy systems with our J2EE systems via
            Inline perl extensions as well as shared libraries written
            in C/C++ that called into the J2EE stack via IIOP.}

          \ressubitem{Created web services layer to facilitate
            interoperability between different technology stacks
            (ruby, java, perl).}

	  \ressubitem{Oversaw development for initial install of HMS
            DataPump software at vendor data center on vendor
            architecture.}

	  \ressubitem{Utilized multiple languages (ruby, clojure,
            perl) to prototype applications and explore the
            feasibility of various applications.}

	  \ressubitem{Developer on project for creating a distributed
            proxy network implemented in php, perl, java and C.}

          \ressubitem{Created java plugins for jboss so that active
            directory users could authenticate with our applications
            as part of a single sign on strategy.}

	\end{ressubsec}

	\begin{ressubsec}{The Sycamore Group}{Fort Washington, PA}{Unix Administrator/Software Developer: November 1999 -- June 2003}

	  \ressubitem{Administered Unix (Sun Solaris) and Linux (Red Hat) servers}

	  \ressubitem{Created B2B web application}

	  \ressubitem{Primary software architect and lead developer
            for VWR Scientific Products ecommerce project developed in
            OO Perl as well as integrating with internal java systems
            and partner web sites. }

	  \ressubitem{Designed and implemented application for the
            design of custom DNA strands (oligos/fretprobes/peptides)
            that integrated with the ecommerce site for ordering. This
            was integrated into the b2b site via SOAP.}

	  \ressubitem{Created and executed plan to load test and
            subsequently tune Netscape Application Server cluster for
            IBN (Investor Broadcast Network). System was subsequently
            able to scale from a hard limit of a few hundred
            simultaneous clients to thousands. Tuning effectively
            removed existing bottlenecks and allowed the same hardware
            to scale to entirely utilize available bandwidth. }

	  \ressubitem{Designed and implemented a single-sign on
            solution for account management and replication for all
            internal users and developers for The Sycamore Group
            Included the installation and configuration of an LDAP
            directory, the design and development of web-based
            administration interfaces. System allowed for single
            source management of Unix and Windows accounts and
            security. Included the integration of corporate mail and
            group discussion system. }

        \end{ressubsec}

	\begin{ressubsec}{SN.com}{Rosemont, PA}{Unix Administrator: 1998-1999}

	  \ressubitem{Configured/Maintained servers}

	  \ressubitem{Administered core application services (dns, mail, http, ldap)}

	  \ressubitem{Planned capacity, ensured fault tolerance}

	\end{ressubsec}

	\begin{ressubsec}{Vertical Net}{Willow Grove, PA}{Unix Administrator: 1997-1998}

	  \ressubitem{performed systems monitoring}

	  \ressubitem{configured core unix services and managed accounts}

	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills}
  
  \resitem{\textbf{Operating Systems:} Linux (Gentoo, Red Hat, and
    Debian), Mac OS X, UNIX (several variants), Windows 98/2000/XP/7}
  
  \begin{reslist}{Computer Languages:}
    
    \ressubitem{Proficient in Java, Perl, C, C++,  UNIX Shells}
    
    \ressubitem{Familiar with \LaTeX, Clojure, Ruby, Python, Objective-c}
    
  \end{reslist}

  \begin{reslist}{Tools and Systems:}
    
    \ressubitem{Proficient in Apache, BIND, CVS/RCS, SVN, Git, Jboss
      (4.x), MySQL, Maven, Make, GnuPG, SSHD, VI, Emacs, NFS, Eclipse}
    
    \ressubitem{Familiar with Kerberos, NFS, OpenLDAP, OpenSSL, Postfix, Samba}
    
  \end{reslist}
  
  
\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Interests/Hobbies}
  
  \resitem{Computer security and cryptography. Created an OS X gui for
    gaining access to servers via portknocking for less technical
    people (specifically, my wife).}

  \resitem{Cloud computing (have AWS account as well as GAE), have
    prototyped basic applications and evaluated leveraging the virtual
    hardware to assist in tasks where we lack infrastructure on hand.}

  \resitem{Iphone and OS X development.}
  
\end{ressection}


\end{document}
